%-------------------------
% Resume in Latex
% Author : Abhinav Kasamsetty
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{url}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% \urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}\textwidth{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEducation}[5]{
  \vspace{-1pt}\item[]
    \begin{tabular*}\textwidth{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
      \small#5
    \end{tabular*}
      % \textbf{\small#6:} #7 \\
}

\newcommand{\resumeProject}[3]{
  \vspace{-1pt}\item[]
    \begin{tabular*}\textwidth{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textbar\space #2 & #3 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingNoBulletListStart}{\begin{itemize}[leftmargin=0pt]}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Abhinav Kasamsetty} & \href{https://abhinavk99.github.io}{abhinavk99.github.io} \\
  \href{mailto:abhinavkasamsetty@gmail.com}{abhinavkasamsetty@gmail.com} & \href{https://www.github.com/abhinavk99}{github.com/abhinavk99} \\
  805-304-6352 & \href{https://www.linkedin.com/in/abhinavkasamsetty/}{linkedin.com/in/abhinavkasamsetty}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingNoBulletListStart
    \resumeEducation
      {The University of Texas at Austin}{Aug 2017 - May 2020}
      {Bachelor of Science in Computer Science}{GPA: 3.90}
      {Concentration in Machine Learning and Artificial Intelligence, Certificate in Japanese}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingNoBulletListStart

    \resumeSubheading
      {Amazon}{Jun 2019 - Aug 2019}
      {Software Development Engineer Intern \textbar\space Amazon Demand Side Platform}{New York, NY}
      \resumeItemListStart
        \resumeItem
          {Designed a scheduling system to manage the number of tests running concurrently across the team's test suites.}
        \resumeItem
          {Developed the system using Java and DynamoDB to handle test runs in queues based on the accessed service.}
        \resumeItem
          {Wrote UI integration tests for the Amazon DSP Console using Selenium in Java.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Jun 2018 - Aug 2018}
      {Software Development Engineer Intern \textbar\space AWS Database Migration Service}{East Palo Alto, CA}
      \resumeItemListStart
        \resumeItem
          {Created an end to end notifications system to notify customers of operational and general information, improving time it takes to make announcements to customers from days to minutes (over 57,000\% faster).}
        \resumeItem
          {Added ability to create/update notifications using a Ruby on Rails front end and a Spring and Oracle DB back end.}
        \resumeItem
          {Developed an interface on the AWS DMS Console for users to read their notifications using React and Typescript.}
        \resumeItem
          {Gained familiarity in using various AWS services, including S3, EC2, and Lambda.}
      \resumeItemListEnd

    \resumeSubheading
      {Vyadvik Inc.}{Jun 2016 - Jul 2016}
      {Intern}{Allen, TX}
      \resumeItemListStart
        \resumeItem
          {Developed a chatbot in JavaScript for a client to show their customers their various household professional services and improve customer support.}
        \resumeItem
          {Used Wit.ai to train an NLP classifier for the chatbot and Twilio to deploy it.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingNoBulletListStart
  
    \resumeProject
      {\href{https://pick-your-prof.herokuapp.com/}{PickYourProf}}{Co-creator, Lead and backend developer}{Oct 2017 - Present}
      \resumeItemListStart
        \resumeItem
          {Cross platform web and mobile application that uses Rate My Professors and the UT Austin grade database to rank professors. Originally created at HackTX 2017 as part of a team.}
        \resumeItem
          {Scraped Rate My Professors, implemented the algorithm in Node.js and Dart, and wrote the backend Express server.}
        \resumeItem
          {\textbf{Technologies Used:} Node.js, Express, Cheerio, HTML/JS/CSS (Bootstrap), SQLite, Flutter, Dart}
      \resumeItemListEnd

    \resumeProject
      {\href{https://github.com/AWConant/jikanpy}{Jikanpy}}{Maintainer, Sole developer}{Apr 2018 - Present}
      \resumeItemListStart
        \resumeItem
          {RESTful API wrapper for the Jikan API for MyAnimeList supporting both synchronous and asynchronous usage.}
        \resumeItem
          {Added static typing using mypy and unit tested with Pytest and VCR.py for 100\% coverage utilizing Travis CI.}
        \resumeItem
          {\textbf{Technologies Used:} Python, Requests, AioHTTP, mypy, Pytest, VCR.py}
      \resumeItemListEnd

    \resumeProject
      {Game of Thrones Relation Extractor}{Co-creator, ML developer}{Feb 2019 - March 2019}
      \resumeItemListStart
        \resumeItem
          {System that extracts relationships between characters on Game of Thrones appearing in wiki pages.}
        \resumeItem
          {Extracted character names and relation triples with named entity recognition and OpenIE using CoreNLP.}
        \resumeItem
          {Handled coreferences using OpenIE and spaCy and stored relation triples in Neo4j.}
        \resumeItem
          {\textbf{Technologies Used:} Python, CoreNLP, OpenIE, spaCy, Neo4j, Wikia API}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-------------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\textbf{Proficient}: Java, Python, Node.js, JavaScript, TypeScript.}
    \resumeSubItem
      {\textbf{Intermediate}: C\texttt{++}, Kotlin, SQL, Dart, Flutter, Jest, Ruby on Rails, Pytest, TestNG.}
    \resumeSubItem
      {\textbf{Basic}: HTML, CSS, \LaTeX, Go, React, Express, Flask, JUnit, Chai, Mocha, Spring, Guice.}
  \resumeSubHeadingListEnd

%-----------AWARDS-------------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem
      {TAMUHack Best Airline Industry Hack - 3rd Place, Thomson Reuters Scholarship, College Scholar}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}