%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    \cventry
    {Senior Software Engineer | Trust and Safety} % Job title
    {Mercari} % Organization
    {Tokyo, Japan} % Location
    {Mar 2023 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Worked on the system that searches for suspicious and fraudulent users based on their account data and activity using Go, Kubernetes, and BigQuery.}
            \item {Designed and developed updates to the microservice warning and applying usage restrictions to users who repeatedly cancel transactions, which improved GMV (gross merchandise value) growth rate by reducing false positives so more users could buy/sell items.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventrythreepositions
    {Software Engineer II | Microsoft Edge Progressive Web Apps}
    {Jan 2022 - Feb 2023}
    {Software Engineer II | Azure Virtual Networking}
    {Aug 2021 - Jan 2022}
    {Software Engineer | Azure Virtual Networking}
    {Aug 2020 - Aug 2021}
    {Microsoft}
    {Redmond, WA}
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Implemented widget APIs so developers can write PWAs, web apps that can be installed to feel/act like native apps, that show widgets in Windows.}
            \item {Added support for PWAs to be launched by opening URLs using C++, React, and TypeScript, helping increase Edge's market share by minutes usage.}
            \item {Designed and prototyped scope extensions for PWAs in Chromium so that web apps with multiple subdomains or TLDs can be installed as one PWA.}
        \end{cvitems}
    }
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Worked on major rewrite of the core system running on millions of servers that programs the networking info for every Azure VM, reducing average VM creation time by over 25\%, using C++ and a publish-subscribe data model to get networking data stored as Protobufs.}
            \item {Designed and implemented support for accessing Azure Private Endpoints from on-premises networks through Azure ExpressRoute FastPath.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Software Development Engineer Intern | Amazon Demand Side Platform} % Job title
    {Amazon} % Organization
    {New York, NY} % Location
    {Jun 2019 - Aug 2019} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and developed a scheduling system to manage the number of tests running concurrently across the team using Java and DynamoDB.}
            \item {Created visualization of current running tests using AWS DynamoDB Streams, Lambda, and S3.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Software Development Engineer Intern | AWS Database Migration Service} % Job title
    {Amazon} % Organization
    {East Palo Alto, CA} % Location
    {Jun 2018 - Aug 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Created an end to end notifications system to inform customers, improving time it takes to notify them from days to minutes (over 57,000\% faster).}
            \item {Added ability for employees to create/update notifications using a Ruby on Rails front end and a Spring and Oracle DB back end.}
            \item {Developed an interface on the AWS DMS Console for users to read their notifications using React and TypeScript.}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
