%-------------------------
% Resume in Latex
% Author : Abhinav Kasamsetty
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{url}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% \urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}\textwidth{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEducation}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}\textwidth{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4
    \end{tabular*}
}

\newcommand{\resumeProject}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}\textwidth{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingNoBulletListStart}{\begin{itemize}[leftmargin=0pt]}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Abhinav Kasamsetty} & \href{https://abhinavk99.github.io}{abhinavk99.github.io} \\
  \href{mailto:abhinavkasamsetty@gmail.com}{abhinavkasamsetty@gmail.com} & \href{https://www.github.com/abhinavk99}{github.com/abhinavk99} \\
  805-304-6352 & \href{https://www.linkedin.com/in/abhinavkasamsetty/}{linkedin.com/in/abhinavkasamsetty}
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingNoBulletListStart

    \resumeSubheading
      {Amazon}{Jun 2019 - Aug 2019}
      {Software Development Engineer Intern \textbar\space Amazon Demand Side Platform}{New York, NY}
      \resumeItemListStart
        \resumeItem
          {Designed a scheduling system to manage the number of tests running concurrently across the team's test suites.}
        \resumeItem
          {Developed the system using Java and DynamoDB to handle test runs in queues based on the accessed service.}
        \resumeItem
          {Wrote UI integration tests for the Amazon DSP Console using Selenium in Java.}
        \resumeItem
          {Created visualization of current running tests using AWS DynamoDB Streams, Lambda, and S3.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Jun 2018 - Aug 2018}
      {Software Development Engineer Intern \textbar\space AWS Database Migration Service}{East Palo Alto, CA}
      \resumeItemListStart
        \resumeItem
          {Created an end to end notifications system to notify customers of operational and general information, improving time it takes to make announcements to customers from days to minutes (over 57,000\% faster).}
        \resumeItem
          {Added ability to create/update notifications using a Ruby on Rails front end and a Spring and Oracle DB back end.}
        \resumeItem
          {Developed an interface on the AWS DMS Console for users to read their notifications using React and Typescript.}
        \resumeItem
          {Gained familiarity in using various AWS services, including S3, EC2, and Lambda.}
      \resumeItemListEnd

    \resumeSubheading
      {The University of Texas at Austin}{Jan 2020 - May 2020}
      {Undergraduate Teaching Assistant \textbar\space CS373: Software Engineering}{Austin, TX}
      \resumeItemListStart
        \resumeItem
          {Held office hours three hours a week to help students with questions about the classwork and the projects.}
        \resumeItem
          {Graded projects, which require looking at students' code style, unit tests, use of AWS/GCP, and databases.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-------------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\textbf{Languages}: Java, Python, JavaScript, C\texttt{++}, Ruby, TypeScript, Kotlin}
    \resumeSubItem
      {\textbf{Technologies/Frameworks}: AWS, Node.js, React, Express, Flask, Rails, PostgreSQL}
    \resumeSubItem
      {\textbf{Testing}: PostgreSQL, Jest, Pytest, TestNG, JUnit, Chai, Mocha}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingNoBulletListStart

    \resumeProject
      {\href{https://www.doctorsearch.me/}{DoctorSearch}}{Oct 2019 - Dec 2019}
      \resumeItemListStart
        \resumeItem
          {Website that provides information about doctors and specialties in 50 major cities and was made by a team of 5.}
        \resumeItem
          {Created RESTful API that supports filtering, sorting, and searching doctors, specialties, and cities, hosted on AWS.}
        \resumeItem
          {\textbf{Technologies Used:} Python, Flask, PostgreSQL, Postman, AWS EB, AWS RDS, Node.js, React, Material UI}
      \resumeItemListEnd

    \resumeProject
      {\href{https://pick-your-prof.herokuapp.com/}{PickYourProf}}{Oct 2017 - Present}
      \resumeItemListStart
        \resumeItem
          {Cross platform web and mobile application that uses Rate My Professors and the UT Austin grade database to rank professors. Originally created at HackTX 2017 by a team.}
        \resumeItem
          {Scraped Rate My Professors, implemented the algorithm in Node.js and Dart, and wrote the backend Express server.}
        \resumeItem
          {\textbf{Technologies Used:} Node.js, Express, Cheerio, HTML/JS/CSS (Bootstrap), SQLite, Flutter, Dart}
      \resumeItemListEnd

    \resumeProject
      {\href{https://pypi.org/project/jikanpy/}{Jikanpy}}{Apr 2018 - Present}
      \resumeItemListStart
        \resumeItem
          {RESTful API wrapper for the Jikan API for MyAnimeList supporting both synchronous and asynchronous usage.}
        \resumeItem
          {Added static typing using mypy and unit tested with Pytest and VCR.py for 100\% coverage utilizing Travis CI.}
        \resumeItem
          {\textbf{Technologies Used:} Python, Requests, AioHTTP, mypy, Pytest, VCR.py}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------AWARDS-------------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem
      {TAMUHack Best Airline Industry Hack - 3rd Place, Thomson Reuters Scholarship, College Scholar}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingNoBulletListStart
    \resumeEducation
      {The University of Texas at Austin}{Aug 2017 - May 2020}
      {Bachelor of Science in Computer Science}{GPA: 3.85}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}